---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rosmosis

[![CRAN
status](https://www.r-pkg.org/badges/version/rosmosis)](https://CRAN.R-project.org/package=rosmosis)
[![B
status](https://github.com/dhersz/rosmosis/workflows/check/badge.svg)](https://github.com/dhersz/rosmosis/actions?query=workflow%3Acheck)
[![Codecov test
coverage](https://codecov.io/gh/dhersz/rosmosis/branch/main/graph/badge.svg)](https://app.codecov.io/gh/dhersz/rosmosis?branch=main)
[![Repo
status](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)

**rosmosis** allows one to download and run
[Osmosis](https://wiki.openstreetmap.org/wiki/Osmosis) from R. Osmosis is a
command line application for processing OpenStreetMap data which consists of
several different pluggable components that can be chained to perform large
operations. The package currently does not aim to offer functions that covers
the entirety of Osmosis' API, and instead offers limited support to running
Osmosis through the `run_osmosis()` function.

## Installation

Development version:

```r
# install.packages("remotes")
remotes::install_github("dhersz/rosmosis")
```

## Usage

Currently, the main (and only) way of using Osmosis with **rosmosis** is through
`run_osmosis()`. This function takes the path to Osmosis and a string listing
the command that should be sent to it.

Let's see how it works using the sample data bundled with the package. In the
following code snippet, we use the function to crop a PBF file using a bounding
box. We also use the `osmosis_path()` function, that looks for a previously
cached Osmosis application and returns its path, downloading it if necessary.

```{r}
library(rosmosis)
library(ggplot2)

cur_osm <- system.file("extdata/cur.osm.pbf", package = "rosmosis")

fs::file_size(cur_osm)

original_pbf <- sf::st_read(cur_osm, layer = "lines", quiet = TRUE)
ggplot(original_pbf) + geom_sf()

output_path <- tempfile("cropped_cur", fileext = ".osm.pbf")

osmosis_command <- paste0(
  "--read-pbf ", cur_osm, " ",
  "--bounding-box ",
  "top=-25.4290 left=-49.2792 bottom=-25.4394 right=-49.2629 ",
  "completeWays=yes ",
  "--write-pbf ", output_path
)

run_osmosis(osmosis_path(), osmosis_command, echo = FALSE, spinner = FALSE)

fs::file_size(output_path)

cropped_pbf <- sf::st_read(output_path, layer = "lines", quiet = TRUE)
ggplot(cropped_pbf) + geom_sf()
```
